Update\_Writeup

### 2019-03-03 R Files/Updated Model/Updates_Writeup.Rmd
Added folders to separate analysis
Fixed wording

Now looking at BMI, there appears to be a linear association between radiation and BMI, with an increase in effective dose as BMI increases. Again, there does not appear to be any relationship between contrast and BMI

From these results, it appears that the amount of radiation and contrast administered to a patient are correlated. Indeed, we find a Pearson's correlation of 0.47, which is significant (t(2380) = 26.05, p < .001).

@@

As with the effective dose model, post hoc analysis using Tukey's HSD for the type of scanner. Here we find that the only significant difference was between the 64SSwIR and 64SSwoIR scanners ($p = .022$). From our model, this difference equates to the 64SSwIR scanners using 6.95 units less contrast than the 64SSwoIR scanners.

>>>>

Now looking at BMI, there appears to be a linear association between radiation and BMI, with an increase in effective dose as BMI increases. Again, there does not appear to be any relationship between contrast and BMI.

@@

As with the effective dose model, post hoc analysis was conducted using Tukey's HSD for the type of scanner. Here we find that the only significant difference was between the 64SSwIR and 64SSwoIR scanners ($p = .022$). From our model, this difference equates to the 64SSwIR scanners using 6.95 units less contrast than the 64SSwoIR scanners.

### 2019-03-03 R Files/Updated Model/Updates_Writeup.tex
Fixed wording

Now looking at BMI, there appears to be a linear association between
radiation and BMI, with an increase in effective dose as BMI increases.
Again, there does not appear to be any relationship between contrast and
BMI

From these results, it appears that the amount of radiation and contrast
administered to a patient are correlated. Indeed, we find a Pearson's
correlation of 0.47, which is significant (t(2380) = 26.05, p
\textless{} .001).

@@

As with the effective dose model, post hoc analysis using Tukey's HSD
for the type of scanner. Here we find that the only significant
difference was between the 64SSwIR and 64SSwoIR scanners (\(p = .022\)).
From our model, this difference equates to the 64SSwIR scanners using
6.95 units less contrast than the 64SSwoIR scanners.

>>>>

Now looking at BMI, there appears to be a linear association between
radiation and BMI, with an increase in effective dose as BMI increases.
Again, there does not appear to be any relationship between contrast and
BMI.

@@

As with the effective dose model, post hoc analysis was conducted using
Tukey's HSD for the type of scanner. Here we find that the only
significant difference was between the 64SSwIR and 64SSwoIR scanners
(\(p = .022\)). From our model, this difference equates to the 64SSwIR
scanners using 6.95 units less contrast than the 64SSwoIR scanners.
